
### Load required packages
```{r load required R packages,message=FALSE}
library(sce)
library(ggplot2)
library(grid)
```


### Ilustrating the general distance sampling scheme

```{r figue 1,fig.cap="Figure 1. Illustrating the general distance sampling scheme"}

x=c(9.4, 2.3, 6.1, 9.8, 6.8, 7.8, 6.0, 4.3, 8.1, 3.4)
y=c(2.4, 4.2, 2.0, 4.5, 5.0, 4.8, 4.1, 2.2, 1.7, 6.9)
xy=data.frame(x=x,y=y)
point_x=7
point_y=3.8

event_x=x[7]
event_y=y[7]


f1=ggplot(xy)+geom_point(aes(x=x,y=y),size=2)+
  geom_segment(aes(x=event_x,y=event_y,xend=x[6],yend=y[6]),
               arrow=arrow(length=unit(0.25,"cm")),colour="red")+
  coord_fixed(ratio = 1)+theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        legend.position='none',
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())

f2=ggplot(xy)+geom_point(aes(x=x,y=y),size=2)+
  geom_segment(aes(x=point_x,y=point_y,xend=x[6],yend=y[6]),
               arrow=arrow(length=unit(0.25,"cm")),colour="red")+
  geom_segment(aes(x=point_x,y=point_y,xend=x[7],yend=y[7]),
               arrow=arrow(length=unit(0.25,"cm")),colour="red")+
  geom_segment(aes(x=point_x,y=point_y,xend=x[3],yend=y[3]),
               arrow=arrow(length=unit(0.25,"cm")),colour="red")+
  geom_segment(aes(x=point_x,y=point_y,xend=x[9],yend=y[9]),
               arrow=arrow(length=unit(0.25,"cm")),colour="red")+
  geom_hline(aes(yintercept=point_y),linetype=2)+
  geom_vline(aes(xintercept=point_x),linetype=2)+
  coord_fixed(ratio = 1)+
  geom_point(aes(x=point_x,y=point_y),size=2,colour="red")+
  theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        legend.position='none',
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())

multiplot(f1,f2,cols=2)
```


### Define the testing proceduce for a given population

Define a test function on all possible distance sampling schemes for the six general population density estimators

```{r Define a test function, warning=FALSE,message=FALSE}
#define the number of focal points should be sampled in each population density estimation
#let's check performance of DPDEs under large distance sample size
nfocals=480
#possible value of k
ks=1:4
#possible value of q
qs=1:4
#number of repeat for each population and each index
rep=30
#number of cpu used
mc.cores=6

TestOnesp=function(nfocals,onesp,ks,qs,rep=10,bordercorrection=0,...){
  win=onesp$win
  sp.ppp=onesp$com
  area=area.owin(win)
  obs=data.frame(x=sp.ppp$x,y=sp.ppp$y)
  #border correction
	border_xmin=win$xrange[1]
	border_xmax=win$xrange[2]
	border_ymin=win$yrange[1]
	border_ymax=win$yrange[2]
	
  validi=1:sp.ppp$n

  if(sp.ppp$n<nfocals){
    nfocals=sp.ppp$n
  }
  etoe_flag=TRUE
  
	Ns=matrix(nrow=rep*length(ks)*length(qs),ncol=6+2)
	Nsi=1
	#repeat different samples of focal points and event 
	for(repi in 1:rep){
		print(repi)
		#calculate estimates of N under different sampling stratigies
		for(k in ks){
			for (q in qs){
				#keep number of total sample distances fixed, nfocals
				nqfocals=round(nfocals/q)
				pfocals=data.frame(x=runif(nqfocals,border_xmin,border_xmax),
						y=runif(nqfocals,border_ymin,border_ymax))
				if(etoe_flag){
					efocali=sample(validi,nqfocals)
					efocals=data.frame(x=sp.ppp$x[efocali],y=sp.ppp$y[efocali])
				}
				#estimateing N by the six general DPDEs
				pr_samples=knq(pfocals,obs,k=k,q=q,type="ptoe")
        #get more distance if there are some NA in pr_samples, which caused by edge effect
        #it works because we treat every distance equally in the population density estimator
        while(any(is.na(pr_samples))){
          fill_index=which(is.na(pr_samples))
          nsfill=length(fill_index)
          pfocals2=data.frame(x=runif(nsfill*2,border_xmin,border_xmax),
  					y=runif(nsfill*2,border_ymin,border_ymax))
          pr_samples2=knq(pfocals2,obs,k=k,q=q,type="ptoe")
          pr_samples2=pr_samples2[!is.na(pr_samples2)]
            oknr=length(pr_samples2)
          if(oknr>=nsfill){
            pr_samples[fill_index]=sample(pr_samples2,nsfill)
          }else if(oknr>0){
            pr_samples[fill_index[1:oknr]]=pr_samples2
          }
        }
          
				N1p_estimate=gsimpleDPDE(pr_samples,k,area)
        Ngp_estimate=gnonrandomDPDE2(pr_samples,"ptoe",k,area)
        
				if(etoe_flag){
					er_samples=knq(efocals,obs,k=k,q=q,type="etoe")
          #get more distances to replace NA
          while(any(is.na(er_samples))){
            fill_index=which(is.na(er_samples))
            nsfill=length(fill_index)
            if( (nsfill*2)< sp.ppp$n){
              efocali2=sample(validi,nsfill*2)
            }else if ((nsfill)< sp.ppp$n){
              efocali2=sample(validi,nsfill)
            }else{
              efocali2=sample(validi,sp.ppp$n)
            }
          
  				  efocals2=data.frame(x=sp.ppp$x[efocali2],y=sp.ppp$y[efocali2])
            er_samples2=knq(efocals2,obs,k=k,q=q,type="etoe")
            er_samples2=er_samples2[!is.na(er_samples2)]
            oknr=length(er_samples2)
            if(oknr>nsfill){
              er_samples[fill_index]=sample(er_samples2,nsfill)
            }else if(oknr>0){
              er_samples[fill_index[1:oknr]]=er_samples2
            }
          }
					N1e_estimate=gsimpleDPDE(er_samples,k,area)
					Nge_estimate=gnonrandomDPDE2(er_samples,"etoe",k,area)
          
					pr_halfi=sample(1:nqfocals,round(nqfocals/2))
					er_halfi=sample(1:nqfocals,nqfocals-length(pr_halfi))
					
					pr_samples_half=pr_samples[pr_halfi,]
					er_samples_half=er_samples[er_halfi,]
					dim(pr_samples_half)=c(length(pr_halfi),q)
					dim(er_samples_half)=c(length(er_halfi),q)
					
					Nc_estimate=gcompositeDPDE(pr_samples_half,er_samples_half,k,area)
          Ncng_estimate=gnrcompositeDPDE(pr_samples_half,er_samples_half,k,area)
				}else{
					Nc_estimate=NA
					N1e_estimate=NA
					Nge_estimate=NA
				}

				#store estiamtions
				Ns[Nsi,]=c(N1p_estimate,N1e_estimate,Nc_estimate,Ngp_estimate,Nge_estimate,
				           Ncng_estimate,attr(Ngp_estimate,"a"),attr(Nge_estimate,"a"))
				Nsi=Nsi+1
			}
		}
	}
	Nsq=rep(qs,times=length(ks)*rep)
	Nsk=rep(rep(ks,each=length(qs)),times=rep)
	Nsrep=rep(1:rep,each=length(qs)*length(ks))
	Ns=cbind(Nsrep,Nsk,Nsq,Ns)
	colnames(Ns)=c("rep","k","q","ptoeN","etoeN","Nc","ptoeNg","etoeNg","NcNg","ap","ae")
	return(Ns)
}
```

### Performance test by simulated populations  

#### Generate the simulated populations

```{r figure 2, fig.cap="Spatial distributions of simulated populations from highly aggregated to almost completely random"}
#the range of the simulated community
win=owin(c(0,100),c(0,100))
#number of simulated population at each aggregative level
npops=30
#number of grids used to generate the simulated population 
nxy=c(20,20)
#intensity of individuals, therefore the expected number individual within the overal range is lam*area=1000
lam=0.1
#aggregated index, the larger the as is, the more aggregate the population is
as=rep(seq(0.01,10,length.out=30),each=npops)

sim_file1="./repo/type1_simulated_populations.RData"
if(!file.exists(sim_file1)){
  type1_sim_pops=list()
  for(i in 1:length(as)){
    #the abundance of the simulated populations in a given size quadrat follows negative binomial distribution
    type1_sim_pops[[i]]=rPopNeg(lam,as[i],win,nxy)
  }
  save(type1_sim_pops,file=sim_file1)
}else{
  load(sim_file1)
}


type=rep(c("k=100","k=0.29","k=0.01"),times=c(type1_sim_pops[[1]]$N,type1_sim_pops[[1+10*npops]]$N,type1_sim_pops[[30*npops]]$N))
x=c(type1_sim_pops[[1]]$com$x,type1_sim_pops[[1+10*npops]]$com$x,type1_sim_pops[[30*npops]]$com$x)
y=c(type1_sim_pops[[1]]$com$y,type1_sim_pops[[1+10*npops]]$com$y,type1_sim_pops[[30*npops]]$com$y)

simpops=data.frame(x=x,y=y,type=type)

ggplot(simpops)+geom_point(aes(x=x,y=y),size=0.5)+
  facet_wrap(~type)+coord_fixed(ratio = 1)+
  theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        legend.position='none',
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())

```

#### Test the performance of the density estimators

once we have the simulated popultions, we can run the test function defined above on each simulated populations
```{r performance test under simulated populations}
#distance to the edge used in border edge correction
bordercorrection=3

simu_re1_file="./repo/type1_simulated_results.RData"
if(!file.exists(simu_re1_file)){
  all_sim1_re=mclapply(type1_sim_pops,TestOnesp,nfocals=nfocals,ks=ks,qs=qs,rep=rep,bordercorrection=bordercorrection,mc.cores=mc.cores)
  save(all_sim1_re,file=simu_re1_file)
  sendmail(recipient="gcshen@des.ecnu.edu.cn",subject="DPDE simulation test by type 1 populations just finished")
}else{
  load(simu_re1_file)
}


```


### Performance test of the DPDE by real tree populations

#### By populations in the BCI
```{r By BCI}
load("./data/BCI_scp_1000by500.RData")
com=BCI
#remove rare species with less than 5 individuals
com=removeRareSpecies(com,minN=5)
#remove a extremely unusual species ANAXPA
com=removeSpecies(com,"ANAXPA")

sp=com$sp
allpops=splitToPopu(com)

#filename="./repo/BCI real results.RData"
filename="./repo/BCI real results final.RData"
if(!file.exists(filename)){
  allre=mclapply(allpops,TestOnesp,nfocals=nfocals,ks=ks,qs=qs,rep=rep,bordercorrection=10,mc.cores=mc.cores)
  #calculate the distance based aggregated index
  HSindexes=numeric()
  for(spi in 1:length(sp)){
   sp.ppp=allpops[[spi]]$com
   nfl=400
   if(nfl>sp.ppp$n)
     nfl=sp.ppp$n
   HSindexes[spi]=mean(replicate(10,HSindex(sp.ppp,nfl)))
  }

  save(allre,HSindexes,file=filename)
  sendmail(recipient="gcshen@des.ecnu.edu.cn",subject="performance test of DPDE on real BCI populations finished")
}else{
  load(filename)
}


```

#### By populations in the HSD
```{r by HSD}
load("./data/HSD_scp.RData")
com2=HSD
#remove rare species with less than 5 individuals
com2=removeRareSpecies(com2,minN=5)

sp2=com2$sp
allpops2=splitToPopu(com2)

#filename2="./repo/HSD real results.RData"
filename2="./repo/HSD real results final.RData"
if(!file.exists(filename2)){
  allre2=mclapply(allpops2,TestOnesp,nfocals=nfocals,ks=ks,qs=qs,rep=rep,bordercorrection=10,mc.cores=mc.cores)
  #calculate the distance based aggregated index
  HSindexes2=numeric()
  for(spi in 1:length(sp2)){
   sp.ppp=allpops2[[spi]]$com
   HSindexes2[spi]=mean(replicate(10,HSindex(sp.ppp,400)))
  }

  save(allre2,HSindexes2,file=filename2)
  sendmail(recipient="gcshen@des.ecnu.edu.cn",subject="performance test of DPDE on real HSD populations finished")
}else{
  load(filename2)
}

```

#### By populations in the TTS
```{r by TTS}
load("./data/TTS_scp.RData")
com3=TTS
#remove rare species with less than 500 individuals
com3=removeRareSpecies(com3,minN=5)

sp3=com3$sp
allpops3=splitToPopu(com3)

#filename3="./repo/TTS real results.RData"
filename3="./repo/TTS real results final.RData"
if(!file.exists(filename3)){
  allre3=mclapply(allpops3,TestOnesp,nfocals=nfocals,ks=ks,qs=qs,rep=rep,bordercorrection=10,mc.cores=mc.cores)
  #calculate the distance based aggregated index
  HSindexes3=numeric()
  for(spi in 1:length(sp3)){
   sp.ppp=allpops3[[spi]]$com
   HSindexes3[spi]=mean(replicate(10,HSindex(sp.ppp,400)))
  }

  save(allre3,HSindexes3,file=filename3)
  sendmail(recipient="gcshen@des.ecnu.edu.cn",subject="performance test of DPDE on real TTS populations finished")
}else{
  load(filename3)
}

```


### Performance of the DPDE on simulated data
```{r figure 3, fig.cap="Performance of the population density estimators by simulated populations"}
#total performance
#the type 1 populations
sim1_RRMSE=matrix(nrow=length(all_sim1_re),ncol=6)

for(i in 1:length(all_sim1_re)){
  sim1_RRMSE[i,]=apply(all_sim1_re[[i]][,-c(1:3)], 2, function(x) RRMSE(type1_sim_pops[[i]]$N,x))
}

estimators=rep(colnames(all_sim1_re[[1]])[-c(1:3)],each=length(all_sim1_re))
sim1_RRMSE=data.frame(estimator=estimators,aggre=rep(as,6),RRMSE=as.vector(sim1_RRMSE))

group1=paste(sim1_RRMSE$aggre,sim1_RRMSE$estimator)
sim1_re=data.frame(aggre=rep(as.numeric(sort(as.character(unique(as)))),each=6),
                   estimator=rep(colnames(all_sim1_re[[1]])[-c(1:3)],length(unique(as))),
                   mean=tapply(sim1_RRMSE$RRMSE,group1,mean),
                   sd=tapply(sim1_RRMSE$RRMSE,group1,sd))

#this two new indexes works not very well, so just remove it from results
del=which( sim1_re$estimator=="NcNg")
sim1_re=sim1_re[-del,]

sim1_re$estimator=as.factor(as.character(sim1_re$estimator))

leglabels=c(expression(italic(lambda[s_ttot])),expression(italic(lambda[n_ttot])),
            expression(italic(lambda[c])),expression(italic(lambda[s_ptot])),
            expression(italic(lambda[n_ptot])))

ggplot(sim1_re,aes(x=aggre,y=mean,color=estimator))+geom_point()+geom_line()+
  geom_errorbar(aes(x=aggre,ymin=mean-sd,ymax=mean+sd))+
  xlab("1/k")+ylab("Mean RRMSE")+
  scale_colour_discrete(name="Estimator",breaks=c("etoeN","etoeNg","Nc","ptoeN","ptoeNg"),labels=leglabels)+
    theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())

```

### Performance of the population density estimator on real data
```{r figure 4, fig.cap="Performance of the population density estimators by real populations"}

focalN=function(onesp,bordercorrection=0){
  win=onesp$win
  sp.ppp=onesp$com

  #border correction
  border_xmin=win$xrange[1]+bordercorrection
	border_xmax=win$xrange[2]-bordercorrection
	border_ymin=win$yrange[1]+bordercorrection
	border_ymax=win$yrange[2]-bordercorrection
	
	validi=sp.ppp$x>border_xmin & sp.ppp$x < border_xmax & 
					sp.ppp$y>border_ymin & sp.ppp$y< border_ymax
  n=sum(validi)
  return(n)
}

com_RRMSE=function(allre,allpops,HSindexes){
real_RRMSE=matrix(nrow=length(allre),ncol=6)
for(i in 1:length(allre)){
  real_RRMSE[i,]=apply((allre[[i]])[,c(4:9)],2,function(x) RRMSE(focalN(allpops[[i]]),x))
}

estimators=rep(colnames(allre[[1]])[c(4:9)],each=length(allpops))
breaks=round(quantile(HSindexes,seq(0,1,length.out=4)),2)
breaks[4]=Inf
HSindex_class=cut(HSindexes,breaks=breaks,include.lowest=TRUE)
real_RRMSE=data.frame(estimator=estimators,
                      aggre=as.factor(rep(HSindex_class,6)),RRMSE=(as.vector(real_RRMSE)))

del=which(real_RRMSE$estimator=="NcNg" )
real_RRMSE=real_RRMSE[-del,]
real_RRMSE$estimator=as.factor(as.character(real_RRMSE$estimator))

real_mean=tapply(real_RRMSE$RRMSE,list(real_RRMSE$estimator,real_RRMSE$aggre),mean)
real_sd=tapply(real_RRMSE$RRMSE,list(real_RRMSE$estimator,real_RRMSE$aggre),sd)

real_RRMSE2=data.frame(estimator=rep(rownames(real_mean),times=dim(real_mean)[2]),
            aggre=(rep(factor(colnames(real_mean),levels=colnames(real_mean)),each=dim(real_mean)[1])),
            RRMSE_mean=as.vector(real_mean),RRMSE_sd=as.vector(real_sd))

real_RRMSE2$ymax=real_RRMSE2$RRMSE_mean+real_RRMSE2$RRMSE_sd
real_RRMSE2$ymin=real_RRMSE2$RRMSE_mean-real_RRMSE2$RRMSE_sd
real_RRMSE2$ymin[real_RRMSE2$ymin<0]=0
return(real_RRMSE2)
}

com_estN=function(allre,allpops){
  meanN_est=unlist(lapply(allre,function(x) apply(x[,c(4:9)],2,mean,na.rm=T)))
estimator=rep(colnames(allre[[1]])[c(4:9)],times=length(meanN_est)/6)
realN=rep(unlist(lapply(allpops,function(x) focalN(x))),each=6)

real_estN=data.frame(realab=realN,estab=meanN_est,ests=estimator)
del=which(real_estN$ests=="NcNg")
real_estN=real_estN[-del,]
real_estN$ests=as.factor(as.character(real_estN$ests))

return(real_estN)
}

bci_RRMSE=com_RRMSE(allre,allpops,HSindexes)
bci_estN=com_estN(allre,allpops)

hsd_RRMSE=com_RRMSE(allre2,allpops2,HSindexes2)
hsd_estN=com_estN(allre2,allpops2)

tts_RRMSE=com_RRMSE(allre3,allpops3,HSindexes3)
tts_estN=com_estN(allre3,allpops3)

all_RRMSE=rbind(bci_RRMSE,hsd_RRMSE,tts_RRMSE)
all_RRMSE$com=rep(c("BCI","HSD","TTS"),times=c(dim(bci_RRMSE)[1],dim(hsd_RRMSE)[1],dim(tts_RRMSE)[1]))
all_estN=rbind(bci_estN,hsd_estN,tts_estN)
all_estN$com=rep(c("BCI","HSD","TTS"),times=c(dim(bci_estN)[1],dim(hsd_estN)[1],dim(tts_estN)[1]))


dodge <- position_dodge(width=0.9)

f41=ggplot(all_RRMSE,aes(x=aggre,y=RRMSE_mean,fill=estimator))+
  geom_bar(position=dodge,stat="identity")+
  geom_errorbar(position=dodge,aes(ymax=ymax,ymin=ymin),width=0.25)+
  xlab("Aggregation index")+ylab("Population Mean RRMSE")+
  scale_fill_discrete(name="Estimator",breaks=c("etoeN","etoeNg","Nc","ptoeN","ptoeNg"),labels=leglabels)+
  coord_cartesian(ylim=c(0,2.1))+facet_wrap(~com,scales="free_x")+
  theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())


f42=ggplot(all_estN)+
  geom_point(aes(x=log(realab),y=log(estab),colour=all_estN$ests))+
  geom_abline(intercept=0,slope=1)+xlab("log(real population size)")+ylab("log(estimated population size)")+
  scale_color_discrete(guide = FALSE)+facet_wrap(~com)+
  theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        legend.position='none',
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())

multiplot(f42,f41)

```

```{r Figure S1,warning=FALSE,message=FALSE,error=FALSE,fig.cap="Figure S1. Performance of the nonrandom estimators for the species whose distributions do not follow the negative binomial distribution"}
#test whether distribution of populations follows negative bionormal distribution
#for BCI plot
ngpvalues=numeric()
for(i in 1:length(allpops)){
  if(allpops[[i]]$com$n>100){
    ncounts=as.numeric(quadratcount(allpops[[i]]$com,nx=1000/20,ny=500/20))
    mu=mean(ncounts)
    size=mu^2/(var(ncounts)-mu)
    temp=try(ks.test(x=ncounts,y=rnbinom(100000,mu=mu,size=size))$p.value)
    if(class(temp)!="try-error"){
      ngpvalues[i]=temp
    }
  }
}

nonpi=which(ngpvalues<0.05)
nonpi=c(13,74,231)

par(mfrow=c(2,2))
par(mai=c(0.1,0.1,0.3,0.1))

plot(allpops[[nonpi[1]]],main="A) Annona acuminata")
plot(allpops[[nonpi[2]]],main="B) Eugenia oerstediana")
plot(allpops[[nonpi[3]]],main="C) Trichilia tuberculata")

estNpi=com_estN(allre[nonpi],allpops[nonpi])[c(4,5,9,10,14,15),]
par(mai=c(0.9,0.9,0.7,0.7))
plot(x=c(5.8,9.5),y=c(5.5,9.7),type="n",
     xlab="Log(real population size)",ylab="Log(Esimated population size)")
points(x=log(estNpi$realab),y=log(estNpi$estab),col=as.numeric(estNpi$ests)+1,pch=rep(c(18,17),time=3))
abline(a=0,b=1,lty=2)
text(x=6.2,y=6.5,labels=c("A"))
text(x=7.5,y=8,labels=c("B"))
text(x=9.35,y=8.8,labels=c("C"))

```


From this figure, the event to event nonrandom DPDE works better under various population distribution.

The relationship between sampling parameters and the performance of the DPDE
```{r}
par_cor=function(all_sim1_re,type1_sim_pops){
  nca1=dim(all_sim1_re[[1]])[1]
typ1=paste(all_sim1_re[[1]][,2],all_sim1_re[[1]][,3])
typlist=unique(typ1)
sim2_RRMSE=matrix(nrow=length(typlist)*length(all_sim1_re),ncol=dim(all_sim1_re[[1]])[2]-3)
for(i in 1:length(all_sim1_re)){
  istart=1+(i-1)*length(typlist)
  iend=i*length(typlist)
  sim2_RRMSE[istart:iend,]=apply(all_sim1_re[[i]][,-c(1:3)], 2, function(x) tapply(1:nca1,typ1,function(y) RRMSE(type1_sim_pops[[i]]$N,x[y])))
}
colnames(sim2_RRMSE)=colnames(all_sim1_re[[1]][,-c(1:3)])
sim2_RRMSE=as.data.frame(sim2_RRMSE)

sim2_RRMSE$k=rep(as.numeric(unlist(lapply(strsplit(unique(typ1)," "),function(x) x[1]))),times=length(all_sim1_re))
sim2_RRMSE$q=rep(as.numeric(unlist(lapply(strsplit(unique(typ1)," "),function(x) x[2]))),times=length(all_sim1_re))

re_ptoeN=summary(lm(ptoeN~k+q,data=sim2_RRMSE))
re_etoeN=summary(lm(etoeN~k+q,data=sim2_RRMSE))
re_Nc=summary(lm(Nc~k+q,data=sim2_RRMSE))
re_ptoeNg=summary(lm(ptoeNg~k+q,data=sim2_RRMSE))
re_etoeNg=summary(lm(etoeNg~k+q,data=sim2_RRMSE))

table1=matrix(nrow=2,ncol=5)
rownames(table1)=c("k","q")
colnames(table1)=colnames(all_sim1_re[[1]][,-c(1:3)])[1:5]
signal=c("-","0","+")
table1[,1]=paste(signal[sign(re_ptoeN$coefficients[-1,1])+2],changeTostar(re_ptoeN$coefficients[-1,4]))
table1[,2]=paste(signal[sign(re_etoeN$coefficients[-1,1])+2],changeTostar(re_etoeN$coefficients[-1,4]))
table1[,3]=paste(signal[sign(re_Nc$coefficients[-1,1])+2],changeTostar(re_Nc$coefficients[-1,4]))
table1[,4]=paste(signal[sign(re_ptoeNg$coefficients[-1,1])+2],changeTostar(re_ptoeNg$coefficients[-1,4]))
table1[,5]=paste(signal[sign(re_etoeNg$coefficients[-1,1])+2],changeTostar(re_etoeNg$coefficients[-1,4]))

  
  return(table1)
} 

table11=par_cor(all_sim1_re,type1_sim_pops)
table12=par_cor(allre,allpops)
table13=par_cor(allre2,allpops2)
table14=par_cor(allre3,allpops3)

table2=rbind(table11,table12,table13,table14)
table2=cbind(rep(c("Simulated","BCI","HSD","TTS"),each=2),table2)
rownames(table2)=NULL
knitr::kable(table2)
```


## comparison between our best nonrandom estimator and other robust methods
```{r comparison between our best nonrandom estimator and other robust methods}
#define the Picard and Bar-Hend's (2007) estimator

#define the likelihood of a Matern point process
pdgamma_x=function(x,R,w,mu,p){
  lambda=w*mu
  m=lambda*pi*x^2
  rz=function(z) {acos(z)-z*sqrt(1-z^2)}
  #the pair correlation function
  gr=function(r) {
    sel=r <= (2*R)
    re=numeric(length=length(r))
    re[sel]=1+2/(w*(pi*R)^2)*rz(r[sel]/2/R)
    re[!sel]=1
    return(re)
  }
  
  jxinner=function(u) rz(u)*u*gr(2*x*u)
  
  jx=16/pi*integrate(jxinner,lower = 0,upper = 1)$value
  
  k=1/(jx-1)
  
  pdkx=-k^2*4/x*(8/pi*integrate(function(u) acos(u)*u*gr(2*x*u),lower = 0,upper = 1)$value -jx)
    
  pdgmma=function(i) dnbinom(i,mu=m,size=k)*(pdkx*(digamma(k+i)-digamma(k)+log(k/(m+k))+(m-i)/(m+k) )+2*i/x-2*lambda*pi*x*(i+k)/(m+k) )
  
  re=sum(unlist(lapply(0:(p-1),pdgmma)))
  
  return(re)
}

#r is the vector of sampled distances
#k is the order neighborhood distance
picard_estimator=function(r,k,area){
  if(inherits(r,"matrix")) r=as.numeric(r)
  
  obj_fun=function(par,r,k) {
    tot=0
    mu=par[1]
    w=par[2]
    R=par[3]
    #browser()
    if(mu<0 | R<0 | w<0) return(Inf)
    
    for(ri in r){
      if(!is.na(ri)){
        tot=tot+sum(log(-pdgamma_x(ri,R,w,mu,k)))
      }
    }
    #tot could be NA
    tot=-tot
    if(tot==Inf | is.na(tot)) tot=9999999999
    
    return(tot)
  }
  #browser()
  N_gest=(length(r)-1)/pi/sum(r[!is.na(r)]^2)
  #maximuize the sum of log likelihood
  est_par=list(convergence=1)
  ntry=0
  while(est_par$convergence!=0 & ntry<=5){
    est_par=try(optim(c(runif(1,1,5),N_gest/runif(1,2,10)/area,runif(1,10,30)),fn=obj_fun,r=r,k=k,control = list(maxit=10000)))
    if(class(est_par)=="try-error"){
      est_par=list(convergence=1)
    }
    ntry=ntry+1
  }
  
  if(est_par$convergence==0){
    return(prod(est_par$par[1:2])*area)
  }else{
    return(NA)
  }
}

PE_estimator=function(r,k,area){
  return(k/pi/median(r^2)*area)
}

#r1 and r2 is the distances to the kth and (k+1)th distance
#each sample size should be divided by 2
KV_estimator=function(r1,r2,k,area){
  return(k/pi/mean(r1)/mean(r2)*area)
}

GP_estimator=function(r,k,area){
  fden=function(alpha,beta,r,k){
    2*pi^k*r^(2*k-1)*gamma(k+alpha)/gamma(alpha)/gamma(k)*beta^(-alpha)*(1/beta+pi*r^2)^(-1*(k+alpha))
  }
  
  obj_fun2=function(par,r,k){
    alpha=par[1]
    beta=par[2]
    if(alpha<=1 | beta<0) return(Inf)
    total=sum(log(fden(alpha,beta,r,k)))
    
    return(-total)
  }
  
  N_gest=(length(r)-1)/pi/sum(r[!is.na(r)]^2)
  est_par=list(convergence=1)
  ntry=0
  while(est_par$convergence!=0 & ntry<=5){
    est_par=optim(c(2,N_gest/2),fn=obj_fun2,r=r,k=k,control = list(maxit=10000))
    ntry=ntry+1
  }
  
  if(est_par$convergence==0){
    return(prod(est_par$par[1:2])*area)
  }else{
    return(NA)
  }
  
}


adaptive_estimator=function(GP,KV,PE,n,k,MV,VR){
  #browser()
  X=matrix(c(1,MV,VR,k,10),5,1)
  #using parameters in the Magnussen et al. 2012
  beta=matrix(c(0,-0.79,-0.5,0,-0.24,-0.15,0,-0.55,-0.47,0,2.31,1.81,0,-1.03,0.22),3,5)
  tp=exp(beta%*%X)
  w1=1/(1+sum(tp[-1]))
  w2=tp[2]*w1
  w3=tp[3]*w1
  return(w1*GP+w2*KV+w3*PE)
}

TestOnesp_other=function(nfocals,onesp,ks,qs,rep=10,bordercorrection=0,...){
  win=onesp$win
  sp.ppp=onesp$com
  area=area.owin(win)
  obs=data.frame(x=sp.ppp$x,y=sp.ppp$y)
  #border correction
	border_xmin=win$xrange[1]
	border_xmax=win$xrange[2]
	border_ymin=win$yrange[1]
	border_ymax=win$yrange[2]
	
  validi=1:sp.ppp$n

  if(sp.ppp$n<nfocals){
    nfocals=sp.ppp$n
  }
  etoe_flag=FALSE
  
	Ns=matrix(nrow=rep*length(ks)*length(qs),ncol=6)
	Nsi=1
	#repeat different samples of focal points and event 
	for(repi in 1:rep){
		print(repi)
		#calculate estimates of N under different sampling stratigies
		for(k in ks){
			for (q in qs){
				#keep number of total sample distances fixed, nfocals
				nqfocals=round(nfocals/q)
				pfocals=data.frame(x=runif(nqfocals,border_xmin,border_xmax),
						y=runif(nqfocals,border_ymin,border_ymax))
				if(etoe_flag){
					efocali=sample(validi,nqfocals)
					efocals=data.frame(x=sp.ppp$x[efocali],y=sp.ppp$y[efocali])
				}
				#estimateing N by the six general DPDEs
				pr_samples=knq(pfocals,obs,k=k,q=q,type="ptoe")
        #get more distance if there are some NA in pr_samples, which caused by edge effect
        #it works because we treat every distance equally in the population density estimator
        while(any(is.na(pr_samples))){
          fill_index=which(is.na(pr_samples))
          nsfill=length(fill_index)
          pfocals2=data.frame(x=runif(nsfill*2,border_xmin,border_xmax),
  					y=runif(nsfill*2,border_ymin,border_ymax))
          pr_samples2=knq(pfocals2,obs,k=k,q=q,type="ptoe")
          pr_samples2=pr_samples2[!is.na(pr_samples2)]
            oknr=length(pr_samples2)
          if(oknr>=nsfill){
            pr_samples[fill_index]=sample(pr_samples2,nsfill)
          }else if(oknr>0){
            pr_samples[fill_index[1:oknr]]=pr_samples2
          }
        }
        
				#get k+1 samples
				pr_samples_k1=knq(pfocals,obs,k=k+1,q=q,type="ptoe")
        #get more distance if there are some NA in pr_samples, which caused by edge effect
        #it works because we treat every distance equally in the population density estimator
        while(any(is.na(pr_samples_k1))){
          fill_index=which(is.na(pr_samples_k1))
          nsfill=length(fill_index)
          pfocals2=data.frame(x=runif(nsfill*2,border_xmin,border_xmax),
  					y=runif(nsfill*2,border_ymin,border_ymax))
          pr_samples_k12=knq(pfocals2,obs,k=k+1,q=q,type="ptoe")
          pr_samples_k12=pr_samples_k12[!is.na(pr_samples_k12)]
            oknr=length(pr_samples_k12)
          if(oknr>=nsfill){
            pr_samples_k1[fill_index]=sample(pr_samples_k12,nsfill)
          }else if(oknr>0){
            pr_samples_k1[fill_index[1:oknr]]=pr_samples_k12
          }
        }
				
				pica_estimate=picard_estimator(pr_samples,k,area) 
				pe_estimate=PE_estimator(pr_samples,k,area)
				gp_estimate=GP_estimator(pr_samples,k,area)
				Ngp_estimate=gnonrandomDPDE2(pr_samples,"ptoe",k,area)
				
				sel=sample(1:length(pr_samples),ceiling(length(pr_samples)/2))
				kv_estimate=KV_estimator(pr_samples[sel],pr_samples_k1[sel],k,area)
				
				#calculate the adaptive estimator by Magnussen et al. 2007
				MV=mean(pr_samples,na.rm=T)/var(pr_samples,na.rm=T)
				VR=(gamma(k)*gamma(k+1)-gamma(k+0.5)^2)/(pi*(length(pr_samples)*k-1)/pi/(mean(pr_samples,na.rm=T))^2*factorial(k-1)*gamma(k))
				adap_estimate=adaptive_estimator(gp_estimate,kv_estimate,pe_estimate,length(pr_samples),k,MV,VR)
				
				#store estiamtions
				Ns[Nsi,]=c(Ngp_estimate,pica_estimate,pe_estimate,kv_estimate,gp_estimate,adap_estimate)
				print(Ns[Nsi,])
				Nsi=Nsi+1
			}
		}
	}
	Nsq=rep(qs,times=length(ks)*rep)
	Nsk=rep(rep(ks,each=length(qs)),times=rep)
	Nsrep=rep(1:rep,each=length(qs)*length(ks))
	Ns=cbind(Nsrep,Nsk,Nsq,Ns)
	colnames(Ns)=c("rep","k","q","Nnp","pica","pe","kv","gp","adap")
	return(Ns)
}



filename="./repo/BCI real other results.RData"
if(!file.exists(filename)){
  allre01=mclapply(allpops,TestOnesp_other,nfocals=nfocals,ks=ks,qs=1,rep=rep,bordercorrection=10,mc.cores=20)
  save(allre01,file=filename)
}else{
  load(filename)
}


filename2="./repo/HSD real other results.RData"
if(!file.exists(filename2)){
  allre201=mclapply(allpops2,TestOnesp_other,nfocals=nfocals,ks=ks,qs=1,rep=rep,bordercorrection=10,mc.cores=20,mc.preschedule=FALSE)
  save(allre201,file=filename2)
}else{
  load(filename2)
}

#filename3="./repo/TTS real results.RData"
filename3="./repo/TTS real other results.RData"
if(!file.exists(filename3)){
  allre301=mclapply(allpops3,TestOnesp_other,nfocals=nfocals,ks=ks,qs=1,rep=rep,bordercorrection=10,mc.cores=10,mc.preschedule=FALSE)
  save(allre301,file=filename3)
}else{
  load(filename3)
}


```



```{r}

com_RRMSE2=function(allre,allpops,HSindexes){
real_RRMSE=matrix(nrow=length(allre),ncol=6)
for(i in 1:length(allre)){
  if(class(allre[[i]])!="try-error"){
    real_RRMSE[i,]=apply((allre[[i]])[,c(4:9)],2,function(x) RRMSE(focalN(allpops[[i]]),x))
  }
}

estimators=rep(colnames(allre[[1]])[c(4:9)],each=length(allpops))
breaks=round(quantile(HSindexes,seq(0,1,length.out=4)),2)
breaks[4]=Inf
HSindex_class=cut(HSindexes,breaks=breaks,include.lowest=TRUE)
real_RRMSE=data.frame(estimator=estimators,
                      aggre=as.factor(rep(HSindex_class,6)),RRMSE=(as.vector(real_RRMSE)))

real_RRMSE$estimator=as.factor(as.character(real_RRMSE$estimator))

real_mean=tapply(real_RRMSE$RRMSE,list(real_RRMSE$estimator,real_RRMSE$aggre),mean,na.rm=T)
real_sd=tapply(real_RRMSE$RRMSE,list(real_RRMSE$estimator,real_RRMSE$aggre),sd,na.rm=T)

real_RRMSE2=data.frame(estimator=rep(rownames(real_mean),times=dim(real_mean)[2]),
            aggre=(rep(factor(colnames(real_mean),levels=colnames(real_mean)),each=dim(real_mean)[1])),
            RRMSE_mean=as.vector(real_mean),RRMSE_sd=as.vector(real_sd))

real_RRMSE2$ymax=real_RRMSE2$RRMSE_mean+real_RRMSE2$RRMSE_sd
real_RRMSE2$ymin=real_RRMSE2$RRMSE_mean-real_RRMSE2$RRMSE_sd
real_RRMSE2$ymin[real_RRMSE2$ymin<0]=0
return(real_RRMSE2)
}

com_estN2=function(allre,allpops){
  meanN_est=unlist(lapply(allre,function(x) apply(x[,c(4:9)],2,mean,na.rm=T)))
estimator=rep(colnames(allre[[1]])[c(4:9)],times=length(meanN_est)/6)
realN=rep(unlist(lapply(allpops,function(x) focalN(x))),each=6)

real_estN=data.frame(realab=realN,estab=meanN_est,ests=estimator)
del=which(real_estN$ests=="gp")
real_estN=real_estN[-del,]
real_estN$ests=as.factor(as.character(real_estN$ests))

return(real_estN)
}

#debug(com_RRMSE2)
bci_RRMSE2=com_RRMSE2(allre01,allpops,HSindexes)
bci_estN2=com_estN2(allre01,allpops)
hsd_RRMSE2=com_RRMSE2(allre201,allpops2,HSindexes2)
hsd_estN2=com_estN2(allre201,allpops2)
tts_RRMSE2=com_RRMSE2(allre301,allpops3,HSindexes3)
tts_estN2=com_estN2(allre301,allpops3)

all_RRMSE2=rbind(bci_RRMSE2,hsd_RRMSE2,tts_RRMSE2)
all_RRMSE2$com=rep(c("BCI","HSD","TTS"),times=c(dim(bci_RRMSE2)[1],dim(hsd_RRMSE2)[1],dim(tts_RRMSE2)[1]))
all_RRMSE2=all_RRMSE2[all_RRMSE2$estimator!="gp",]

all_estN2=rbind(bci_estN2,hsd_estN2,tts_estN2)
all_estN2$com=rep(c("BCI","HSD","TTS"),times=c(dim(bci_estN2)[1],dim(hsd_estN2)[1],dim(tts_estN2)[1]))

all_RRMSE2$estimator=factor(all_RRMSE2$estimator,levels = c("adap","kv","pe","pica","Nnp"))
all_estN2$ests=factor(all_estN2$ests,levels=c("adap","kv","pe","pica","Nnp"))

levels(all_estN2$ests)=c("italic(lambda[adap])","italic(lambda[kv])",
            "italic(lambda[pe])",
            "italic(lambda[pica])",
            "italic(lambda[n_ptot])")


leglabels2=c(expression(italic(lambda[adap])),expression(italic(lambda[kv])),
            expression(italic(lambda[pe])),
            expression(italic(lambda[pica])),
            expression(italic(lambda[n_ptot])))






dodge=position_dodge(width=0.9)


f4101=ggplot(all_RRMSE2[all_RRMSE2$estimator!="gp",],aes(x=aggre,y=RRMSE_mean,fill=estimator))+
  geom_bar(position=dodge,stat="identity")+
  geom_errorbar(position=dodge,aes(ymax=ymax,ymin=ymin),width=0.25)+
  xlab("Aggregation index")+ylab("Population Mean RRMSE")+
  scale_fill_discrete(name="Estimator",breaks=c("adap","kv","pe","pica","Nnp"),labels=leglabels2)+
  facet_wrap(~com,scales="free_x")+
  theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())


f4201=ggplot(all_estN2)+
  geom_point(aes(x=log(realab),y=log(estab)),alpha=0.2)+
  geom_abline(intercept=0,slope=1)+xlab("log(real population size)")+ylab("log(estimated population size)")+
  scale_color_discrete(guide = FALSE)+facet_wrap(~ests,ncol=5,labeller = label_parsed)+
  theme_bw()+
  theme(plot.margin=unit(rep(1,4),"lines"),
        legend.position='none',
        panel.grid.minor=element_blank(),
        panel.grid.major=element_blank())

multiplot(f4201,f4101)


```

Here is the R session information for above analyses
```{r}
sessionInfo()
```
